### 2018-12-14 tex/paper.tex
Corrections for pairwise Potts model done.

\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/potts_chain_extension.png}
\mycaption{\footnotesize \em An illustration of the worst-case optimal
submodular extension for Potts model for a chain graph of 4 variables, each of
which can take 3 labels. The figure shows the way to compute the extension
values of the set $A = \{v_{1, 1}, v_{4, 1}, v_{3, 2}$\}.}
\label{fig:alternate}
\end{figure}

@@

\end{proof}
\vspace{-1mm}

Proposition \ref{proposition:potts_worst-case optimal} paves the way for us to
identify the worst-case optimal extension for hierarchical Potts model, which
we discuss in the following section.

@@

However, using the equivalence of relaxed LP objectives and the Lovasz
extension of submodular extensions in proposition
\ref{proposition:potts_equiv}, we are able to compute $s^*$ in ${\mathcal
O}(NL)$ time. Specifically, we use the algorithm of
Ajanthan et al. \citep{ajanthan2017efficient}, which provides an efficient filtering procedure to compute the subgradient of the LP relaxation objective $E({\bf y})$ of (P-LP).\\
%
\vspace{-0.5cm}
{\proposition Computing the subgradient of $E({\bf y})$ in (P-LP) is equivalent to computing the conditional gradient for the submodular function $F_{Potts}$. \label{proposition:subgrad}} 
\newline(Proof in appendix).
\begin{proof}
  For the Potts model, we derived the worst-case optimal extension $F_{Potts}$ by
  making its Lovasz extension $f({\bf y})$ same as the objective function
    $E({\bf y})$ of the worst-case optimal LP relaxation. Hence, we have
\begin{align}
    E({\bf y}) &= f({\bf y})  \nonumber \\
    {} &=  \max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle.\nonumber
\end{align}

>>>>

\begin{figure}
\centering
\includegraphics[scale = 0.30]{./figures/potts_chain_extension.png}
\mycaption{\footnotesize \em An illustration of the worst-case optimal
submodular extension for Potts model for a chain graph of 4 variables, each of
which can take 3 labels. The figure shows the way to compute the extension
values of the set $A = \{v_{1, 1}, v_{4, 1}, v_{3, 2}$\}.}
\label{fig:potts_extension_example}
\end{figure}

@@

\end{proof}
\vspace{-1mm}
Proposition \ref{proposition:potts_worst-case optimal} paves the way for us to identify the worst-case optimal extension for hierarchical Potts model, which we discuss in the following section. Figure (\ref{fig:potts_extension_example}) shows an example where we compute $F_{Potts}(A)$ for a small graph and a given set $A$ representing an invalid labeling. Figure (\ref{fig:optimal_extension_graph}) shows the $st$-graph representation of $F_{Potts}$ for a small instance.

@@

However, using the equivalence of relaxed LP objectives and the Lovasz
extension of submodular extensions in proposition
\ref{proposition:potts_equiv}, we are able to compute $s^*$ in ${\mathcal
O}(NL)$ time. Specifically, we use the algorithm of
Ajanthan et al. \citep{ajanthan2017efficient}, which provides an efficient filtering procedure to compute the subgradient of the LP relaxation objective $E({\bf y})$ of (P-LP).\\
%
\vspace{-0.5cm}
{\proposition Computing the subgradient of $E({\bf y})$ in (P-LP) is equivalent to computing the conditional gradient for the submodular function $F_{Potts}$. \label{proposition:subgrad}} 
\begin{proof}
  For the Potts model, we derived the worst-case optimal extension $F_{Potts}$ by
  making its Lovasz extension $f({\bf y})$ same as the objective function
    $E({\bf y})$ of the worst-case optimal LP relaxation. Hence, we have
\begin{align}
    E({\bf y}) &= f({\bf y})  \nonumber \\
    {} &=  \max_{{\bf s} \in EP(F)} \langle {\bf y}, {\bf s} \rangle.\nonumber
\end{align}
